\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{times}
\usepackage{tocloft}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage[utf8]{inputenc}
\usepackage{tabularx}
\title{kamloic-cv}
%-----------------------------------------------------------
%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars


%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}


%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

%-----------------------------------------------------------  
  \textbf{\Large Kameni Loïc } & \\
  Solutions Architect & \\
  Barcelona, Spain  \\
  loickam@gmail.com \\
\end{tabular*}
\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Work Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item
	\ressubheading{MongoDB}{Barcelona, ES}{Solutions Architect}{Feb. 2024 - Present}
	\begin{itemize}
		\resitem{Communicating the technical and business value of MongoDB by supporting sales with in-depth technical discovery, solution architecture, demos, and comprehensive technical documentation.}
		\resitem{Driving demand by participating in technical workshops and account-based marketing events, while demonstrating strong problem-solving skills and resilience in addressing complex business challenges.}
	\end{itemize}

\item 
	\ressubheading{VMware}{Barcelona, ES}{Solutions Engineer}{Jul. 2022 - Feb. 2024}
	\begin{itemize}
		\resitem{Architecting and presenting VMware technology solutions, focusing on scalability, performance, and meeting complex business challenges.}
		\resitem{Providing technical guidance and support to partner teams to streamline customer lifecycle management and ensure successful deployment and integration.}
	\end{itemize}

\item
	\ressubheading{VMware}{Paris, FR}{Tanzu, Solutions Engineer}{Mar. 2022 - Jul. 2022}
	\begin{itemize}
		\resitem{Building and deploying scalable cloud-native applications using Agile methodologies across Docker, Kubernetes, and local environments.}
		\resitem{Implementing CI/CD pipelines for automated and efficient application deployment across multiple targets.}
		
	\end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item
	\ressubheading{HEI Junia}{Lille, FR}{MEng. Computer Science}{2017 - 2022}
	\begin{itemize}
		\resitem{Software engineering, Embedded programming and Project Management}
		\resitem{Data sciences, Mathematics and ML/AI}
	\end{itemize}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Languages \& Computer Skills}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}

		\resitem{{\bf Languages:} {\bf French} (Native) - {\bf English} (bilingual proficiency) - {\bf Spanish} (Elementary proficiency)}
		\resitem{{\bf IT Skills:} {\bf Cloud:} Azure, AWS, Docker, Kubernetes - {\bf DevOps:} Terraform, GitHub Actions, Java, Python, Linux, SQL, Kafka}
  
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Interests}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}

		\resitem{{\bf Sports:} Football - Tennis - Golf }
		\resitem{{\bf Blog:} Writing a personal blog that translates my life experiences through data, visualization, and insights {\bf (him.com).}}
  
\end{itemize}

\end{document}